The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

###Research Question  
Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?

@@

A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact both the  entrepreneurship rate and the rate of career-change within a given country.

>>>>

###Research Question  
Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

@@

A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact the rate of entrepreneurship within the country.
